---
title: "Kim_birds_MA"
author: "ML"
date: "26/06/2031"
output: html_document
editor_options: 
  chunk_output_type: console
---

*NOTE:* code not tested for knitting.   

```{r setup, cache = F, echo=FALSE, results = FALSE}
knitr::opts_chunk$set(error = TRUE) #allow some execution errors
knitr::opts_chunk$set(eval = TRUE, echo = TRUE, warning = FALSE)
sessionInfo()
```

```{r prepare, message = FALSE, echo = TRUE, eval = FALSE, warning = FALSE}
install.packages("tidyverse")
install.packages("ape")
install.packages("curl")
install.packages("fulltext")
install.packages("treebase")
install.packages("devtools")
devtools::install_github("ropensci/rotl", dependencies = TRUE, build_vignette=TRUE)
install.packages("rotl")
install.packages("readxl")
```

```{r load packages, message = FALSE, echo = TRUE, eval = TRUE, warning = FALSE}
library(tidyverse)
library(ape, curl)
library(rotl)
library(readxl)
```

```{r load data, message = FALSE, echo = TRUE, eval = TRUE, warning = FALSE}
dat <- read.csv("dat_23_06_2023.csv")
dim(dat)
names(dat)

myspecies <- as.character(unique(dat$FocalSpL)) #get list of unique species from FocalSpL column
#str_sort(myspecies) #visual check
length(myspecies) #89 species
#length(unique(myspecies)) #89 unique species names

#rotl - Warning message: Troglodytes aedon aedon, Troglodytes aedon musculus are not matched - replace
myspecies <- replace(myspecies, myspecies == "Troglodytes aedon musculus", "Troglodytes musculus")
myspecies <- replace(myspecies, myspecies == "Troglodytes aedon aedon", "Troglodytes aedon")
myspecies <- unique(myspecies)
length(myspecies) #88 species
```

## Using *rotl* package to retrieve synthetic species tree from Open Tree of Life

Rotl is an R package (https://peerj.com/preprints/1471/) allowing access to synthetic phylogenetic tree available at Open Tree of Life database (https://opentreeoflife.org/).   

```{r rotl find species, message = FALSE, echo = TRUE, eval = TRUE, warning = FALSE, }
taxa <- tnrs_match_names(names = myspecies, context_name = "Birds")
dim(taxa) #88 species - all matched
table(taxa$approximate_match) #5 approximate matches
taxa[taxa$approximate_match==TRUE, ] ##5 species with typos in their names - fix in the main data set!
#               search_string              unique_name approximate_match  ott_id is_synonym flags number_matches
# 3           malothrus mater           Molothrus ater              TRUE  213450      FALSE                    1
# 4      tetrastes sewesrzowi      Tetrastes sewerzowi              TRUE 3596073      FALSE                    1
# 9         puffinus pacificu         Ardenna pacifica              TRUE  471653      FALSE                    1
# 81 aphelocoma coerulescents  Aphelocoma coerulescens              TRUE  175629      FALSE                    1
# 86  thamnomanes schisogynus Thamnomanes schistogynus              TRUE  381762      FALSE                    1
```


Fix species names in the data file - as a new Species column.
```{r correct specis names data, message = FALSE, echo = TRUE, eval = TRUE, warning = FALSE}
names(dat)

dat$FocalSpL_corrected <- (dat$FocalSpL) #get list of unique species from FocalSpL column
length(unique(dat$FocalSpL_corrected)) #89 species

#rotl - Warning message: Troglodytes aedon aedon, Troglodytes aedon musculus are not matched - replace
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Troglodytes aedon musculus", "Troglodytes musculus")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Troglodytes aedon aedon", "Troglodytes aedon")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Malothrus mater", "Molothrus ater")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Tetrastes sewesrzowi", "Tetrastes sewerzowi")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Puffinus pacificu", "Ardenna pacifica")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Aphelocoma coerulescents", "Aphelocoma coerulescens")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Thamnomanes schisogynus", "Thamnomanes schistogynus")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Vermivora celata", "Leiothlypis celata")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Oreothlypis celata", "Leiothlypis celata")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Parus montanus", "Poecile montanus")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Oceanodroma leucorhoa", "Hydrobates leucorhous")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Anas strepera", "Mareca strepera")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Columbina squammata", "Scardafella squammata")
dat$FocalSpL_corrected <- replace(dat$FocalSpL_corrected, dat$FocalSpL_corrected == "Parus ater", "Periparus ater")

length(unique(dat$FocalSpL_corrected)) #87 species

# save modified data file
write.csv(dat, "dat_23_06_2023_ML.csv")
```

Check the species list using rotl.   

```{r rotl find species, message = FALSE, echo = TRUE, eval = TRUE, warning = FALSE, }
myspecies <- as.character(unique(dat$FocalSpL_corrected)) #get list of unique species from FocalSpL_corrected column
taxa <- tnrs_match_names(names = myspecies, context_name = "Birds")
dim(taxa) #87 species - all matched
#table(taxa$approximate_match) #no approximate matches
```

Get the initial tree.  

```{r rotl species tree, warning = FALSE, results=FALSE}
tree <- tol_induced_subtree(ott_ids = taxa[["ott_id"]], label_format = "name")  
plot(tree, cex=.6, label.offset =.1, no.margin = TRUE)

tree$tip.label <- gsub(" \\(.*", "", tree2$tip.label) #remove comments
tree$tip.label <- gsub("_"," ", tree2$tip.label) #get rid of the underscores
length(tree$tip.label) #87
```

Check matching species and labels.

```{r re-check tree labels}
myspecies <- unique(dat$FocalSpL_corrected)
treespecies <- tree$tip.label

#check overlap and differences with taxa list
intersect(myspecies, treespecies) # overlap
setdiff(myspecies, treespecies) # in data, not in tree - mostly synonyms
setdiff(treespecies, myspecies) # in tree, not in data - mostly synonyms

#check if the tree is really binary 
is.binary(tree) #TRUE
# tree_binary$node.label <- NULL #you can delete internal node labels
# *NOTE:* no branch lengths are included, they can be created later via simulations.   
```

Save tree

```{r save final tree}
write.tree(tree, file="Kim_birds_MA.tre") #save the tree

# *NOTE:* underscores within species names on tree tip labals are added automatically
# tree <- read.tree(file="plot_cooked_fish_MA.tre") #if you need to read in the tree
# tree$tip.label <- gsub("_"," ", tree$tip.label) #get rid of the underscores
# tree$node.label <- NULL #you can delete internal node labels
```

Plot tree

```{r plot final binary tree, fig.width=10, fig.height=20, echo=TRUE, message=FALSE}
#plot(tree, cex=.6, label.offset =.1, no.margin = TRUE)

#or plot to pdf
pdf("plot_tree.pdf", width=8, heigh=12)
plot(tree, cex=0.6, label.offset =.1, no.margin = TRUE)
dev.off()
```



