---
title: "**Integration of multimodal cues does not alter mean but reduces variance in avian responses to predators: a systematic review and meta-analysis**"
author: "**Kim + Shinichi et al.**"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 3
    toc-title: "**Table of Contents**"
    output-file: "index.html"
    theme: simplex
    embed-resources: true
    code-fold: true
    code-tools: true
    number-sections: true
    #bibliography: ./bib/ref.bib
    fontsize: "12"
    max-width: "10"
    code-overflow: wrap
crossref: 
  fig-title: Figure     # (default is "Figure")
  tbl-title: Table     # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.    # (default is "Table")
editor_options: 
  chunk_output_type: console
execute:
  warning: false
  message: false
  tidy: true
  cache: true
---

## Setting up

```{r}
#install.packages("pacman")
#pacman::p_load(devtools, tidyverse, metafor, patchwork, R.rsp, emmeans)

#devtools::install_github("daniel1noble/orchaRd", force = TRUE)

library(tidyverse)
library(here)
library(lme4)
library(orchaRd)
#library(gptstudio)
library(metafor)
library(patchwork)
library(alluvial)
library(ggalluvial)
library(easyalluvial)
library(ape)
library(clubSandwich)
library(emmeans)
library(MuMIn)
library(kableExtra)
# making metafor talk to MuMIn
eval(metafor:::.MuMIn)
# install.packages("pak")
#pak::pak("MichelNivard/gptstudio")
```

## Getting data loaded

```{r}
#dat_full <- read.csv(here("data/dat_04_04_2023.csv"))
#dat_full <- read.csv(here("data/dat_28_06_2023.csv"))
dat_full <- read.csv(here("data/dat_19_07_2023.csv"))

# add phylogenetic tree - only topologies
# TODO? - we could get better tree from birdtree.org
# we can do 50 different trees as in 
# https://academic.oup.com/sysbio/article/68/4/632/5267840
tree_top <- read.tree(here("R/birds_MA.tre"))

# tree with branch lengths
tree <- compute.brlen(tree_top)
#plot(tree)
# turning it into a correlation matrix
cor_tree <- vcv(tree,corr=T)
```

## Custom functions

```{r}
# custom functions

#' Title: Contrast name generator
#'
#' @param name: a vector of character strings
cont_gen <- function(name) {
  combination <- combn(name, 2)
  name_dat <- t(combination)
  names <- paste(name_dat[, 1], name_dat[, 2], sep = "-")
  return(names)
}

#' @title get_pred1: intercept-less model
#' @description Function to get CIs (confidence intervals) and PIs (prediction intervals) from rma objects (metafor)
#' @param model: rma.mv object 
#' @param mod: the name of a moderator 
get_pred1 <- function (model, mod = " ") {
  name <- firstup(as.character(stringr::str_replace(row.names(model$beta), mod, "")))
  len <- length(name)
  
   if (len != 1) {
        newdata <- matrix(NA, ncol = len, nrow = len)
        for (i in 1:len) {
            pos <- which(model$X[, i] == 1)[[1]]
            newdata[, i] <- model$X[pos, ]
        }
        pred <- metafor::predict.rma(model, newmods = newdata)
    }
    else {
        pred <- metafor::predict.rma(model)
  }
  estimate <- pred$pred
  lowerCL <- pred$ci.lb
  upperCL <- pred$ci.ub 
  lowerPR <- pred$cr.lb
  upperPR <- pred$cr.ub 
  
  table <- tibble(name = factor(name, levels = name, labels = name), estimate = estimate,
                  lowerCL = lowerCL, upperCL = upperCL,
                  pval = model$pval,
                  lowerPR = lowerPR, upperPR = upperPR)
}

#' @title get_pred2: normal model
#' @description Function to get CIs (confidence intervals) and PIs (prediction intervals) from rma objects (metafor)
#' @param model: rma.mv object 
#' @param mod: the name of a moderator 
get_pred2 <- function (model, mod = " ") {
  name <- as.factor(str_replace(row.names(model$beta), 
                                paste0("relevel", "\\(", mod,", ref = name", "\\)"),
                                ""))
  len <- length(name)
  
  if(len != 1){
  newdata <- diag(len)
  pred <- predict.rma(model, intercept = FALSE, newmods = newdata[,-1])
  }
  else {
    pred <- predict.rma(model)
  }
  estimate <- pred$pred
  lowerCL <- pred$ci.lb
  upperCL <- pred$ci.ub 
  lowerPR <- pred$cr.lb
  upperPR <- pred$cr.ub 
  
  table <- tibble(name = factor(name, levels = name, labels = name), estimate = estimate,
                  lowerCL = lowerCL, upperCL = upperCL,
                  pval = model$pval,
                  lowerPR = lowerPR, upperPR = upperPR)
}

#' @title mr_results
#' @description Function to put results of meta-regression and its contrasts
#' @param res1: data frame 1
#' @param res1: data frame 2
mr_results <- function(res1, res2) {
  restuls <-tibble(
    `Fixed effect` = c(as.character(res1$name), cont_gen(res1$name)),
    Estimate = c(res1$estimate, res2$estimate),
    `Lower CI [0.025]` = c(res1$lowerCL, res2$lowerCL),
    `Upper CI  [0.975]` = c(res1$upperCL, res2$upperCL),
    `P value` = c(res1$pval, res2$pval),
    `Lower PI [0.025]` = c(res1$lowerPR, res2$lowerPR),
    `Upper PI  [0.975]` = c(res1$upperPR, res2$upperPR),
  )
}


#' @title all_models
#' @description Function to take all possible models and get their results
#' @param model: intercept-less model
#' @param mod: the name of a moderator 

all_models <- function(model, mod = " ", type = "homo") {
  
  # getting the level names out
  level_names <- levels(factor(model$data[[mod]]))
  dat2 <- model$data

  VCV1 <- vcalc(vi = dat2$Vd,
             cluster = dat2$SubjectID,
             rho = 0.5)
  #model$data[[mod]] <- factor(model$data[[mod]], ordered = FALSE)
  # meta-regression: contrasts 
  # helper function to run metafor meta-regression
  run_rma1 <- function(name) {
    rma.mv(yi = SMD, 
         V = VCV1, 
         mods = ~ relevel(dat2[[mod]], ref = name), 
         random = list(~1 | FocalSpL,
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat2)
   }

    run_rma2 <- function(name) {
    rma.mv(yi = SMD, 
         V = VCV1, 
         mods = ~ relevel(dat2[[mod]], ref = name), 
         random = list(~1 | FocalSpL,
                             ~1 | RecNo,
                             ~gsub("\"", "", mod) | Obs_ID),
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat2)
   }

  # results of meta-regression including all contrast results; taking the last level out ([-length(level_names)])

  if (type == "homo"){
  model_all <- map(level_names[-length(level_names)], run_rma1)
  } 
  else {
  model_all <- map(level_names[-length(level_names)], run_rma2)
  }
  
  # getting estimates from intercept-less models (means for all the groups)
  res1 <- get_pred1(model, mod = mod)
  
  # getting estiamtes from all contrast models
  res2_pre <- map(model_all, ~ get_pred2(.x, mod = mod))
  
  # a list of the numbers to take out unnecessary contrasts
  contra_list <- Map(seq, from=1, to=1:(length(level_names) - 1))
  res2 <- map2_dfr(res2_pre, contra_list, ~.x[-(.y), ]) 
  # creating a table
  res_tab <- mr_results(res1, res2) %>% 
  kable("html",  digits = 3) %>%
  kable_styling("striped", position = "left") %>%
  scroll_box(width = "100%")
  
  # results
  res_tab

}

# test 
#all_models(mod1, mod = "Treat_mod")
#all_models(mod1s, mod = "Treat_mod")
```

## Preparing data set

```{r}
# function for calculating variance
Vd_func <- function(d, n1, n2, design, r = 0.5){
  # independent design
  if(design == "among"){
    var <- (n1 + n2) / (n1*n2) + d^2 / (2 * (n1 + n2 - 2)) # variance
  } else { # dependent design
    var <- 2*(1-r) / n1 + d^2 / (2*(n1 - 1)) # variance
  }
  var # return variance
}

# getting Hedges' g - get small size bias corrected effect size
dat_full$SMD <- dat_full$d / (1 - 3/(4 * (dat_full$NTreat + dat_full$Ncontrol) - 9))

# flipping d 
dat_full$SMD <- dat_full$d*dat_full$Direction*dat_full$PredictedDirection


# calucating Vd
dat_full$Vd <- with(dat_full, pmap_dbl(list(SMD, NTreat, Ncontrol, Design), Vd_func))


# extra useful function
# function for getting mean and sd from median, quartiles and sample size
# get_mean_sd <- function(median, q1, q3, n){
#   sd <- (q3 - q1) / (2 * (qnorm((0.75 * n - 0.125) / (n + 0.25)))) # sd
#   mean <- (median + q1 + q3)/3 # mean
#   c(mean, sd)
# }


# observation id
dat_full$Obs_ID <- 1:nrow(dat_full)
dat_full$Phylo <- gsub(" ", "_", dat_full$FocalSpL)

# filtering very large variance and also very small sample size
dat_int <- dat_full %>% filter(Vd < 10 & Ncontrol > 2 & NTreat > 2)

#dim(dat_full)
#dim(dat_int)


# sorting out modality stuff
# creat - 1,2,3 modality - also easier classification A, O, V (AOV = L) 

dat_int %>% mutate(Treat_mod = case_when(Treatment == "A" ~ "A",
                                          Treatment == "AV" ~ "AV",
                                          Treatment == "AVG" ~ "AV",
                                          Treatment == "AVM" ~ "AV",
                                          Treatment == "L" ~ "AVO",
                                          Treatment == "O" ~ "O",
                                          Treatment == "OV" ~ "OV",
                                          Treatment == "V" ~ "V",
                                          Treatment == "VG" ~ "V",
                                          Treatment == "VM" ~ "V",
                                          Treatment == "VP" ~ "V"),
                    # into how many
                    Treat_No = case_when(Treatment == "A" ~ 1,
                                         Treatment == "AV" ~ 2,
                                         Treatment == "AVG" ~ 2,
                                         Treatment == "AVM" ~ 2,
                                         Treatment == "L" ~ 3,
                                         Treatment == "O" ~ 1,
                                         Treatment == "OV" ~ 2,
                                         Treatment == "V" ~ 1,
                                         Treatment == "VG" ~ 1,
                                         Treatment == "VM" ~ 1,
                                         Treatment == "VP" ~ 1),
                    # des it have some add-ons
                    Add_on = case_when(Treatment == "A" ~ "No",
                                         Treatment == "AV" ~ "No",
                                         Treatment == "AVG" ~ "Yes",
                                         Treatment == "AVM" ~ "Yes",
                                         Treatment == "L" ~ "No",
                                         Treatment == "O" ~ "No",
                                         Treatment == "OV" ~ "No",
                                         Treatment == "V" ~ "No",
                                         Treatment == "VG" ~ "Yes",
                                         Treatment == "VM" ~ "Yes",
                                         Treatment == "VP" ~ "Yes"),

                      ) -> dat

# creating data just for A, V, and AV 
dat_short <- dat %>% filter(Treat_mod == "A" | Treat_mod == "V" | Treat_mod == "AV")

# for add-on, we only need V and AV
dat_short_add <- dat %>% filter(Treat_mod == "AV" | Treat_mod == "V")


dat <- dat %>%
  mutate_if(is.character, as.factor)

# reordering factors for better visualisation

# dat$Treat_mod <- factor(dat$Treat_mod, levels = c("A", "V", "AV", "O", "OV", "AVO"))

```

## Exploratory visualization 


For `Treat_mod` (Treatment), we will only visualise `A`, `V`, and `AV` as `O` $r $, `OV`, and `AVO` are much rarer. But for `Type` (Trait type), we will use all data.

::: {.panel-tabset}

## Treatment vs. Trait types
```{r}
# reordering dat_shrot$Treat_mod for better visualisation
dat_short$Treat_mod <- factor(dat_short$Treat_mod, levels = c("A", "V", "AV"))

# Treatment vs Type
dat_short %>% group_by(Treat_mod, Type) %>%
  summarise(n = n()) -> tab

#alluvial(tab1[,1:2], freq = tab1$n)

# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Treat_mod,
           axis2 = Type)) +
  geom_alluvium(aes(fill = Treat_mod)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Treatment modality and trait type")

```

## Treatment vs. Treatment duration
```{r}
# tuning Treatment duration into a binary variable
dat_short %>% mutate(TDration = case_when(duration_days < 1 ~ "< 1 day",
                                          duration_days >= 1 ~ "> 1 day")) -> dat_short

# reformatting data
dat_short %>% group_by(Treat_mod, TDration) %>%
  summarise(n = n()) -> tab

# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Treat_mod,
           axis2 = TDration)) +
  geom_alluvium(aes(fill = Treat_mod)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Treatment modality and duration of treatment")

```


## Treatment vs. Sex

```{r}
 # Treat_mod vs Design

dat_short %>% group_by(Treat_mod, Sex) %>%
  summarise(n = n()) -> tab
#alluvial(tab1[,1:2], freq = tab1$n)

# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Treat_mod,
           axis2 = Sex)) +
  geom_alluvium(aes(fill = Treat_mod)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Treatment modality and study setting")
```

## Treatment vs. Predator type

```{r}

# Treat_mod vs Design
dat_short %>% filter(PredTo != "") %>%
  group_by(Treat_mod, PredTo) %>%
  summarise(n = n()) -> tab

tab$PredTo <- factor(tab$PredTo, levels = c("A", "N", "B"), labels = c("Adult", "Nestling", "Both"))

#alluvial(tab1[,1:2], freq = tab1$n)

# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Treat_mod,
           axis2 = PredTo)) +
  geom_alluvium(aes(fill = Treat_mod)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Treatment modality and study setting")
```


## Treatment vs. Design

```{r}
 # Treat_mod vs Design

dat_short %>% group_by(Treat_mod, Design) %>%
  summarise(n = n()) -> tab
#alluvial(tab1[,1:2], freq = tab1$n)

# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Treat_mod,
           axis2 = Design)) +
  geom_alluvium(aes(fill = Treat_mod)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Treatment modality and study setting")
```

## Treatment vs. Season

```{r}
 # Treat_mod vs Design

dat_short %>% group_by(Treat_mod, Season) %>%
  summarise(n = n()) -> tab
#alluvial(tab1[,1:2], freq = tab1$n)

# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Treat_mod,
           axis2 = Season)) +
  geom_alluvium(aes(fill = Treat_mod)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Treatment modality and study setting")
```


## Treatment vs. Setting

```{r}
 # Treat_mod vs Design

dat_short %>% group_by(Treat_mod, Setting) %>%
  summarise(n = n()) -> tab
#alluvial(tab1[,1:2], freq = tab1$n)

# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Treat_mod,
           axis2 = Setting)) +
  geom_alluvium(aes(fill = Treat_mod)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Treatment modality and study setting")
```


## Treatment vs Control type

```{r}

# Treat_mod vs ControlType

dat_short %>% filter(ControlType != "mix") %>% group_by(Treat_mod, ControlType) %>%
  summarise(n = n()) -> tab
#alluvial(tab1[,1:2], freq = tab1$n)

# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Treat_mod,
           axis2 = ControlType)) +
  geom_alluvium(aes(fill = Treat_mod)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 6, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Treatment modality and control type")

```


## Trait type vs. Treatment duration
```{r}
# Type vs duration_days

# turn duration_days into a binary factor: less than 1 and more than 1

dat %>% mutate(TDration = case_when(duration_days < 1 ~ "< 1 day",
                                          duration_days >= 1 ~ "> 1 day")) -> dat


dat %>% group_by(Type, TDration) %>%
  summarise(n = n()) -> tab2

# using ggaruvial
ggplot(tab2,
       aes(y = n,
           axis1 = Type,
           axis2 = TDration)) +
  geom_alluvium(aes(fill = Type)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Trait type and duration of treatment")

```

## Trait type vs. Sex
```{r}
# Type vs duration_days

# turn duration_days into a binary factor: less than 1 and more than 1

dat %>% mutate(TDration = case_when(duration_days < 1 ~ "< 1 day",
                                          duration_days >= 1 ~ "> 1 day")) -> dat

dat %>% group_by(Type, Sex) %>%
  summarise(n = n()) -> tab

# reordering
tab$Sex <- factor(tab$Sex, levels = c("F", "M", "both"), labels = c("Female", "Male", "Both"))


# using ggaruvial
ggplot(tab,
       aes(y = n,
           axis1 = Type,
           axis2 = Sex)) +
  geom_alluvium(aes(fill = Type)) +
  geom_stratum(alpha = 0.5) +
  geom_text(stat = "stratum", size = 4, aes(label = after_stat(stratum))) +
  theme(legend.position = "none") +
  theme(legend.position = "none",
        axis.text.x = element_blank()) + # remove x-axis labels
  ylab("Frequency") + 
  xlab("Trait type and duration of treatment")

```

:::

## Meta-analysis

### All random effects

```{r}
##| warning: false
# VCV matrix

VCV <- vcalc(vi = dat$Vd,
             cluster = dat$SubjectID,
             rho = 0.5)

mod0 <- rma.mv(yi = SMD,
       V = VCV, 
       random = list(#~1 | Phylo,
                     ~1 | FocalSpL,
                     ~1 | RecNo,
                     ~1 | SubjectID, # incoprated as VCV
                     ~1 | Obs_ID),
      # R = list(Phylo = cor_tree),
       test = "t",
       method = "REML", 
       sparse = TRUE,
       data = dat)

summary(mod0)

# TODO - think about whether we add this or not
robust(mod0, cluster = dat$SubjectID)

round(i2_ml(mod0), 2)

orchard_plot(mod0,
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)",
             branch.size = 3)

```

### Reduced model

```{r}
# reduced model

mod0r <- rma.mv(yi = SMD,
       V = VCV, 
       random = list(~1 | FocalSpL,
                     ~1 | RecNo,
                     ~1 | Obs_ID),
       test = "t",
       method = "REML", 
       sparse = TRUE,
       data = dat)

summary(mod0r)

round(i2_ml(mod0r), 2)

# comparing two models
#anova(mod0, mod0r)
```

## Meta-regression: uni-moderator (mostly)

### Treatmeant with all data

```{r}
## Treatment - A, V, AV etc 
#dat$Phylo <- as.character(dat$Phylo)
#match(dat$Phylo, colnames(cor_tree))
#match(colnames(cor_tree), dat$Phylo)

mod1 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1 | FocalSpL,
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mod = ~ Treat_mod - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

summary(mod1)

round(r2_ml(mod1)*100, 2)

orchard_plot(mod1, 
             mod = "Treat_mod",
             group = "RecNo", 
             xlab = "Standardised mean differnece (SMD)",
             branch.size = 3)

# result table
all_models(mod1, mod = "Treat_mod")
```

### Treatment with Audio and Visual data

#### Homoscedastic model

```{r}

VCVs <- vcalc(vi = dat_short$Vd,
             cluster = dat_short$SubjectID,
             rho = 0.5)


mod1s <- rma.mv(yi = SMD,
                   V = VCVs,
                   random = list(~1|FocalSpL,
                                 ~1 | RecNo,
                                 ~1 | Obs_ID),
                   mod = ~ Treat_mod - 1, 
                   test = "t",
                   method = "REML", 
                   sparse = TRUE,
                   data = dat_short)

summary(mod1s)

round(r2_ml(mod1s)*100, 2)

orchard_plot(mod1s, 
             mod = "Treat_mod",
             group = "RecNo", 
             xlab = "Standardised mean differnece (SMD)",
             branch.size = 3)

# result table
all_models(mod1s, mod = "Treat_mod")
```

#### Heteroscedastic model

```{r}
# modeling heteroscedasticity
mod1s2 <- rma.mv(yi = SMD, 
                V = VCVs, 
                random = list(~1|FocalSpL , 
                              ~1 | RecNo, 
                              ~ Treat_mod | Obs_ID), 
                mod = ~ Treat_mod, 
                test = "t",
                struct = "DIAG",
                method = "REML", 
                sparse = TRUE,
                data = dat_short)

summary(mod1s2)

orchard_plot(mod1s2, 
             mod = "Treat_mod",
             group = "RecNo", 
             xlab = "Standardised mean differnece (SMD)",
             branch.size = 3)
```


#### Comparing models

```{r}
# comparision models
anova(mod1s, mod1s2)
```

### Treatment with some additions

```{r}
# the effect of additions
# this is a part of sensitivity analysis

VCVs2 <- vcalc(vi = dat_short_add$Vd,
             cluster = dat_short_add$SubjectID,
             rho = 0.5)

mod5 <- rma.mv(yi = SMD, 
                V = VCVs2, 
                random = list(~1|FocalSpL , 
                              ~1 | RecNo, 
                              ~ Treat_mod | Obs_ID), 
                mod = ~ Treat_mod*Add_on - 1,
                test = "t",
                struct = "DIAG",
                method = "REML", 
                sparse = TRUE,
                data = dat_short_add)

summary(mod5)
```

### Treatment as an ordinal variable

```{r}
# testing the number of stimuli

mod4 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo, 
                             ~1 | Obs_ID), 
               mod = ~ Treat_No, 
               test = "t",
               method = "REML", 
               sparse = TRUE,
               data = dat)

summary(mod4)

bubble_plot(mod4,
             mod = "Treat_No",
             group = "RecNo",
             xlab = "The number of simuli",
             g = TRUE)

```

### Trait type

```{r}
# Type of responses
mod2 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1 | FocalSpL,
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mod = ~ Type - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

summary(mod2)

mod2c <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL,
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mod = ~ Type,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

summary(mod2c)

mod2d <- rma.mv(yi = SMD,
               V = VCV,
               random = list(~1|FocalSpL,
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mod = ~ relevel(Type, ref = "LifeHistory"),
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

summary(mod2d)

orchard_plot(mod2,
             mod = "Type",
             group = "RecNo", 
             xlab = "Standardised mean differnece (SMD)",
             branch.size = 3)

round(r2_ml(mod2)*100, 2)

# heteroscadasticity model
mod2b <- rma.mv(yi = SMD, 
               V = VCV, 
               mod = ~ Type - 1, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo, 
                             ~Type | Obs_ID), 
               struct = "DIAG",
               test = "t",
               method = "REML", 
               sparse = TRUE,
               data = dat)

summary(mod2b)


# make other hetero
mod2e <- rma.mv(yi = SMD,
               V = VCV,
               mod = ~ Type, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo, 
                             ~Type | Obs_ID), 
               struct = "DIAG",
               test = "t",
               method = "REML", 
               sparse = TRUE,
               data = dat)

summary(mod2e)

mod2f <- rma.mv(yi = SMD,
               V = VCV,
               mod = ~ relevel(Type, ref = "LifeHistory"), 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo, 
                             ~Type | Obs_ID), 
               struct = "DIAG",
               test = "t",
               method = "REML", 
               sparse = TRUE,
               data = dat)

summary(mod2f)

# heteroscadasticity model better than the homoscedasticity model
# note LifeHistory has lowest variation but this may be expected? 
# as it is less flexiable (e.g. the number of eggs?)
anova(mod2, mod2b)

orchard_plot(mod2b, 
             mod = "Type",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)",
             branch.size = 3)
```

### Trait categories

```{r}

# Category of responses

mod3 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo, 
                             ~1 | Obs_ID), 
               mod = ~ Category - 1, 
               test = "t",
               method = "REML", 
               sparse = TRUE,
               data = dat)

summary(mod3)

round(r2_ml(mod3)*100, 2)

orchard_plot(mod3, 
             mod = "Category",
             group = "RecNo", 
             xlab = "Standardised mean differnece (SMD)",
             angle = 45,
             branch.size = 3)
```

### Predactor guild

```{r}
# Predactor guild
# quite heterogeneous
# TODO this could be in random effects - think abou thtis a bit later
mod6 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ PredGuild - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

summary(mod6)

round(r2_ml(mod6)*100, 2)

orchard_plot(mod6, 
             mod = "PredGuild",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")
```

### Setting

```{r}
# Setting

mod7 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ Setting - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

summary(mod7)

round(r2_ml(mod7)*100, 2)

orchard_plot(mod7, 
             mod = "Setting",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")
```

### Season

```{r}
# Season

mod8 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ Season - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

mod8b <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ Season,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

summary(mod8b)

round(r2_ml(mod8)*100, 2)

orchard_plot(mod8,
             mod = "Season",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")
```

### Design

```{r}
# Design
mod9 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ Design - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)
summary(mod9)


mod9b <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ Design,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)

summary(mod9b)

round(r2_ml(mod9)*100, 2)

orchard_plot(mod9,
             mod = "Design",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")
```

### Response period

```{r}
# Response period
mod10 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ ResponsePeriod - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)
summary(mod10)

round(r2_ml(mod10)*100, 2)

orchard_plot(mod10,
             mod = "ResponsePeriod",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")
```

### Control type

```{r}
# control type
mod11 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ ControlType - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)
summary(mod11)

round(r2_ml(mod11)*100, 2)

orchard_plot(mod11,
             mod = "ControlType",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")

```

### Sex

```{r}
# sex
# TODO - this could be interesting
# what is in males and females
mod12 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ Sex - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)
summary(mod12)

round(r2_ml(mod12)*100, 2)

orchard_plot(mod12,
             mod = "Sex",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")

# shoter data for just males and females
# hetero but no sex effect here
dat_sex <- dat %>% filter(Sex != "both")

VCV3 <- vcalc(vi = dat_sex$Vd,
             cluster = dat_sex$SubjectID,
             rho = 0.5)

mod12a <- rma.mv(yi = SMD, 
                 V = VCV3, 
                 mod = ~ Sex, 
                 random = list(~1|FocalSpL , 
                               ~1 | RecNo, 
                               ~1 | Obs_ID), 
                 #struct = "DIAG",
                 test = "t",
                 method = "REML", 
                 sparse = TRUE,
                 data = dat_sex)

mod12b <- rma.mv(yi = SMD, 
                V = VCV3, 
                mod = ~ Sex, 
                random = list(~1|FocalSpL , 
                              ~1 | RecNo, 
                              ~Sex | Obs_ID), 
                struct = "DIAG",
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dat_sex)

summary(mod12b)

anova(mod12a, mod12b)

orchard_plot(mod12b,
             mod = "Sex",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")

```

### Age

```{r}
# age
mod13 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ Age - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)
summary(mod13)

round(r2_ml(mod13)*100, 2)

orchard_plot(mod13,
             mod = "Age",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")
```

### Predactor type

```{r}
# type of predator

dat$PredTo[dat$PredTo == ""] <- NA
mod14 <- rma.mv(yi = SMD, 
               V = VCV, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ PredTo - 1,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)
summary(mod14)

round(r2_ml(mod14)*100, 2)

orchard_plot(mod14,
             mod = "PredTo",
             group = "RecNo",
             xlab = "Standardised mean differnece (SMD)")

```

### Treatment duration

```{r}

# treatment duration

dat$ln_duration <- log(dat$duration_days)

mod15 <- rma.mv(yi = SMD,
               V = VCV,
               random = list(~1|FocalSpL,
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ ln_duration,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)
summary(mod15)

mod16 <- rma.mv(yi = SMD,
               V = VCV,
               random = list(~1|FocalSpL,
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ ln_duration*Type,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat)
summary(mod16)

round(r2_ml(mod15)*100, 2)

bubble_plot(mod15,
             mod = "ln_duration",
             group = "RecNo",
             xlab = "log(duration in days)",
             g = TRUE) +
    geom_point(data = dat,
    aes(x = ln_duration, y = SMD,
    color = Type,
    fill = Type,
    size = 1/sqrt(Vd)), alpha = 0.6) +
    scale_color_discrete() + #+ # how to put the legend for colour
    guides(color = "legend")

#p + geom_point(aes(colour = Type))
#scale_colour_manual(values = c("red", "blue", "green"))

```

## Meta-regression: multi-moderator (mostly)

### full models

```{r}
#######################
# Mulit-variable models
#######################

dat_short$sln_duration <- scale(log(dat_short$duration_days))

mod_full <- rma.mv(yi = SMD, 
               V = VCVs, 
               random = list(~1|FocalSpL , 
                             ~1 | RecNo,
                             ~1 | Obs_ID),
               mods =  ~ #Design +
                         sln_duration*Type +
                         sln_duration*Treat_mod +
                         Sex,
               test = "t",
               method = "REML",
               sparse = TRUE,
               data = dat_short)
summary(mod_full)

round(r2_ml(mod_full)*100, 2)

orchard_plot(mod_full,
             mod = "Type",
             group = "RecNo", 
             xlab = "Standardised mean differnece (SMD)",
             branch.size = 3)

orchard_plot(mod_full,
             mod = "Treat_mod",
             group = "RecNo", 
             xlab = "Standardised mean differnece (SMD)",
             branch.size = 3)

int_type <- mod_results(mod_full, mod = "sln_duration", group = "RecNo", weights = "prop",
                                   by = "Type")

bubble_plot(int_type, group = "RecNo", mod = "sln_duration", xlab = "ln(duration in days)",
                     legend.pos = "top.left", condition.nrow = 3)

int_trt <- mod_results(mod_full, mod = "sln_duration", group = "RecNo", weights = "prop",
                        by = "Treat_mod")

bubble_plot(int_trt, group = "RecNo", mod = "sln_duration", xlab = "ln(duration in days)",
            legend.pos = "top.left", condition.nrow = 3)
```

```{r}
# mulit-model selection
candidates <- dredge(mod_full, trace = 2)

# displays delta AICc <2
candidates_aic2 <- subset(candidates, delta < 5) 
# model averaging
mr_averaged_aic2 <- summary(model.avg(candidates, delta < 5)) 

# relative importance of each predictor for all the models
importance <- sw(candidates)
```

## Publication bias

### Funnel plot: uni-moderator

```{r}

```

### Funnel plot: multi-moderator

```{r}
funnel(mod0r, 
       yaxis="seinv",
       type = "rstudent")
```

```{r}
funnel(mod_full, 
       yaxis="seinv",
       type = "rstudent")
```

### Egger regression: uni-moderator

```{r}
# Egger

dat$effectN <- (dat$Ncontrol * dat$NTreat) / (dat$Ncontrol + dat$NTreat)
dat$sqeffectN <- sqrt(dat$effectN)

mod0e <- rma.mv(yi = SMD,
                V = VCV,
                mods = ~ sqeffectN,
                random = list(#~1 | Phylo,
                  ~1 | FocalSpL,
                  ~1 | RecNo,
                  #~1 | SubjectID, # incoprated as VCV
                  ~1 | Obs_ID),
                #R = list(Phylo = cor_tree),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dat)

summary(mod0e)

bubble_plot(mod0e,
            mod = "sqeffectN",
            group = "RecNo",
            xlab = "Effective N",
            g = TRUE)
```

### Decline effect: uni-moderator

```{r}
# decline effect
mod0d <- rma.mv(yi = SMD,
                V = VCV,
                mods = ~ Year,
                random = list(#~1 | Phylo,
                  ~1 | FocalSpL,
                  ~1 | RecNo,
                  #~1 | SubjectID, # incoprated as VCV
                  ~1 | Obs_ID),
                #R = list(Phylo = cor_tree),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dat)

summary(mod0d)

bubble_plot(mod0d,
            mod = "Year",
            group = "RecNo",
            xlab = "Publication year",
            g = TRUE)

```

### All together

```{r}
# full model
dat_short$effectN <- (dat_short$Ncontrol * dat_short$NTreat) / (dat_short$Ncontrol + dat_short$NTreat)
dat_short$sqeffectN <- sqrt(dat_short$effectN)

mod_fulle <- rma.mv(yi = SMD, 
                   V = VCVs, 
                   random = list(~1|FocalSpL , 
                                 ~1 | RecNo,
                                 ~1 | Obs_ID),
                   mods =  ~ sqeffectN +
                     Year +
                     sln_duration*Type +
                     sln_duration*Treat_mod +
                     Sex,
                   test = "t",
                   method = "REML",
                   sparse = TRUE,
                   data = dat_short)
summary(mod_fulle)

dat_fulle <- qdrg(object = mod_fulle, 
                  data = dat_short)
# marginalized overall mean at vi = 0 and year.c = 0; also weights = "prop" or "cells" average things over proportionally. if not specified, all groups (levels) get the same weights
# res_fulle1 <- emmeans(dat_fulle, 
#                      specs = ~ sqeffectN,
#                      df = mod_fulle$ddf, 
#                      weights = "prop")
```
